\tool

### 2017-11-20 paper/paper.tex
These are no longer the projects we will use

\section{Introduction}
%Importance
Tool discovery is a problem... \\

@@

\begin{table}
	\centering
	\caption{Evaluation Projects}
	\begin{tabular}{|l|l|l|c|}
		\hline
		\textbf{Project} & \textbf{Java Files} & \textbf{LOC} & \textbf{Pull Requests} \\
		\hline
		spring-boot\footnote{https://github.com/spring-projects/spring-boot.git} &  &  & \\
		\hline
		dubbo\footnote{https://github.com/alibaba/dubbo.git} &  &  & \\
		\hline
		guava\footnote{https://github.com/google/guava.git}  &  &  & \\
		\hline
		retrofit\footnote{https://github.com/square/retrofit.git}  &  &  & \\
		\hline
		rocketmq\footnote{https://github.com/apache/rocketmq.git}  &  &  & \\
		\hline
		\end{tabular}
	\begin{tablenotes}
        \item[1] Details on projects used for study including GitHub repository name, number of Java files, lines of Java code, and total pull requests.
    \end{tablenotes}
	\label{tools}
\end{table}

Table~\ref{tools} presents the projects used for evaluating \tool~in our study and provides details about each repository. These repositories span a wide range of organizations and real-world software applications, including a system to create ``stand-alone, production-grade'' Spring applications~\cite{spring-boot}, a high-performance remote procedure call framework from Chinese e-commerce company Alibaba~\cite{dubbo}, a collection of core Google libraries~\cite{guava}, an HTTP client for Android financial services mobile application Square~\cite{square-retrofit}, and a distributed messaging and data-streaming platform by Apache~\cite{rocketmq}.

>>>>

\section{Introduction}
%Importance
Software contains many tools and features designed to make users more efficient and effective in their work. However, despite a wide availability of such useful tools many are often ignored or because users do not know of their existence.\\

@@

\begin{table}
	\centering
	\caption{Evaluation Projects}
	\begin{tabular}{|l|l|l|c|}
		\hline
		\textbf{Project} & \textbf{Java Files} & \textbf{LOC} & \textbf{Pull Requests} \\
		\hline
%		spring-boot\footnote{https://github.com/spring-projects/spring-boot.git} &  &  & \\
%		\hline
%		dubbo\footnote{https://github.com/alibaba/dubbo.git} &  &  & \\
%		\hline
%		guava\footnote{https://github.com/google/guava.git}  &  &  & \\
%		\hline
%		retrofit\footnote{https://github.com/square/retrofit.git}  &  &  & \\
%		\hline
%		rocketmq\footnote{https://github.com/apache/rocketmq.git}  &  &  & \\
%		\hline
		\end{tabular}
	\begin{tablenotes}
        \item[1] Details on projects used for study including GitHub repository name, number of Java files, lines of Java code, and total pull requests.
    \end{tablenotes}
	\label{tools}
\end{table}
